Efficient Coalition Formation for Web Services

### 2013-03-13 papers/coalition/coalition.tex
Changes

In this paper, we propose a cooperative game theory based model for aggregation of web services within communities. The solution concepts of cooperative game theory seeks to find most efficient ways of forming coalitions (teams) of agents, maximizing their gain and payoff, and also distributing gain in a fair way to keep coalitions stable by having all agents satisfied. We first propose a representation function for communities of web services based on their qualities and capacities. Using this function we can evaluate the $worth$ of each community of web services. Our community managers facing new membership requests, analyses whether the new coalition having the new set of web services will keep the community stable for $all$ web services already residing in the community or not. The community manager will reject the membership requests if it finds out new coalition would be unstable, preventing $any$ subset of web services from gaining significantly more by deviating and joining other communities. Also web services facing communities, will try to join communities which maximizes their gain, if they find out they can deviate and gain more, they will form new coalitions with other communities. The cooperative game theory solution methods are combinatorial in nature and are NP-complete, making them impractical in real world applications; however, using the concepts of coalition stability we have offered approximation algorithms running in polynomial time providing web services and community managers with applicable and near-optimal decision making mechanisms.

@@

\emph{1) Web services} are rational entities providing services to end users. They aim to maximize their individual income by receiving enough requests from end users. In order to increase their revenue, web services seek for more tasks if they have the capacity and throughput. Web services can join communities to have better efficiency collabrating with others, have access to higher market share and opportunity to receive a bigger task pool from end users. The way the web services reside inside communities and how communities of web services are engineered is described thoroughly in \cite{DBLP:journals/ijebr/MaamarSTBB09}. Throughout this paper, in our equations, we refer to web services as $ws$.

>>>>

In this paper, we propose a cooperative game theory based model for aggregation of web services within communities. The solution concepts of cooperative game theory seeks to find most efficient ways of forming coalitions (teams) of agents, maximizing their gain and payoff, and also distributing gain in a fair way to keep coalitions stable by having all agents satisfied. We first propose a representation function for communities of web services based on their qualities and capacities. Using this function we can evaluate the $worth$ of each community of web services. Our community managers facing new membership requests, analyses whether the new coalition having the new set of web services will keep the community stable for $all$ web services already residing in the community or not. The community manager will reject the membership requests if it finds out new coalition would be unstable, preventing $any$ subset of web services from gaining significantly more, by deviating and joining other communities. Also web services facing communities, will try to join communities which maximizes their gain, if they find out they can deviate and gain more, they will form new coalitions with other communities. The cooperative game theory solution methods are combinatorial in nature and are NP-complete, making them impractical in real world applications; however, using the concepts of coalition stability we have offered approximation algorithms running in polynomial time providing web services and community managers with applicable and near-optimal decision making mechanisms.

@@

\emph{1) Web services} are rational entities providing services to end users. They aim to maximize their individual income by receiving enough requests from end users. In order to increase their revenue, web services seek for more tasks if they have the capacity and throughput. Web services can join communities to have better efficiency by collaborating with others, to have access to higher market share and to have opportunity of receiving a bigger task pool from end users. The way the web services reside inside communities and how communities of web services are engineered is described thoroughly in \cite{DBLP:journals/ijebr/MaamarSTBB09}. Throughout this paper, in our equations, we refer to web services as $ws$.
